Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-03-23 ms.tex
replace 217 GHz vs 857 GHz scatterplot with figure including additional Planck bands

@@

\begin{figure}
\begin{center}
\epsfig{file=scatter_857_217.eps, width=3.4in}
\caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
GHz. Left: before correcting for offset and residual Solar dipole. Right: after
correcting or the best-fit offset and dipole amplitude, as described in 
$\S$\ref{sec:zp}. The dashed red line shows the best-fit linear relationship
between 857 GHz and 217 GHz.}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\epsfig{file=dipole_all.eps, width=3.4in}
\caption{\label{fig:dip}  Scatter plots of \PLANCK~143, 217, 353, and 545 GHz 
versus \PLANCK~857 GHz. Left: before correcting for offset and residual Solar 
dipole. Right: after correcting or the best-fit offset and dipole amplitude, as
described in $\S$\ref{sec:zp}. The dashed red line shows the best-fit linear 
relationship in each case.}
\end{center}
\end{figure}

@@

%\begin{figure}
%\begin{center}
%\epsfig{file=scatter_857_217.eps, width=3.4in}
%\caption{\label{fig:scatter} Scatter plot of \PLANCK~217 GHz versus \PLANCK~857
%GHz. Left: before correcting for offset and residual Solar dipole. Right: after
%correcting or the best-fit offset and dipole amplitude, as described in 
%$\S$\ref{sec:zp}. The dashed red line shows the best-fit linear relationship
%between 857 GHz and 217 GHz.}
%\end{center}
%\end{figure}
